Irt plot extra

### 2023-01-03 manuscript_v2.Rmd
EFA assumptions

We checked the sampling adequacy by applying Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy on the EFA sample (n=`r nrow(EFA.data)`) [@kaiserIndexFactorialSimplicity1974]. The overall KMO value for 48 items was `r printnum(KMO$MSA)`, which exceeded the cut-off value (.50), indicating an adequate sample size [@hutchesonMultivariateSocialScientist1999]. Additionally, Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`)=`r apa(bartlet$chisq, 2, T)`, p \< .001 implied that the correlations between items were adequate for conducting the EFA. However, only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than \|.30\|., and the inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`. Figure \@ref(fig:efa-plot-print)-A depicts the respective correlation matrix.

>>>>

We checked the post-hoc sampling adequacy by applying Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy on the EFA sample (n=`r nrow(EFA.data)`) [@kaiserIndexFactorialSimplicity1974]. KMO>0.50 would indicate adequate sample size [@hutchesonMultivariateSocialScientist1999]. Results indicated that we had an adequate sample size (KMO=`r printnum(KMO$MSA)`). Additionally, we investigate the quality of the correlation matrix by Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954] prior to conduct the EFA. Results indicated that the correlatio matrix was adequate to conduct EFA ($\chi^2$ (`r bartlet$df`)=`r apa(bartlet$chisq, 2, T)`, p< .001). However,`r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than |0.30|, and the inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`. Figure \@ref(fig:efa-plot-print)-A depicts the respective correlation matrix.
